---
title: "Activity 6 - Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
```



```{r}

resume <- read_csv("https://www.openintro.org/data/csv/resume.csv")

head(resume)

summary(resume)

```


```{r}
library(dplyr)

glimpse(resume)

```

- By looking into this data, it is an Observational experiment study thats observing the pattern and statistics behind candidates resume shortlisting and employement ratio

class(resume$received_callback)
-received_callback this variable is a numeric variable that stores 0 & 1 values if 0 then resume not shortlisted if 1 then selected for interview as per assumption

- received_callback : data visualization using {ggplot2}

```{r}

plot <- ggplot(resume, aes(x = received_callback))

plot + geom_bar()

plot + geom_histogram()

```


```{r}

library(dplyr)

#counts and percentages
summary_table <- resume %>%
  count(received_callback) %>%
  mutate(percent = prop.table(n) * 100)

colnames(summary_table) <- c("received_callback", "n", "percent")

print(summary_table)


```

```{r}

library(ggplot2)

# counts and percentages
counts <- table(resume$received_callback)
percentages <- prop.table(counts) * 100

# Create a data frame for plotting
data_plot <- data.frame(
  received_callback = factor(names(counts), levels = names(counts)),
  n = as.vector(counts),
  percent = as.vector(percentages)
)

# bar plot
ggplot(data_plot, aes(x = received_callback, y = n)) +
  geom_bar(stat = "identity", fill = "Blue") +
  geom_text(aes(label = paste0(percent, "%")), vjust = -0.5, color = "white") +
  labs(x = "Received Callback", y = "Count") +
  ggtitle("Counts and Percentages for Received Callback") +
  theme_minimal()


```

```{r}
library(dplyr)

# Calculate the logistic equation
logistic_eq <- glm(received_callback ~ ., data = resume, family = binomial())

logistic_eq

```




```{r}
# Sample mapping of first names to race categories
library(dplyr)

# Group the data by race and calculate the percentage of calls received
race_percentage <- resume %>%
  group_by(race) %>%
  summarize(percentage = mean(received_callback == 1) * 100)

# Print the result for Yes
print(race_percentage)

# Group the data by race and calculate the percentage of calls received
race_percentage <- resume %>%
  group_by(race) %>%
  summarize(percentage = mean(received_callback == 0) * 100)
```


```{r}
# For No
print(race_percentage)


```


```{r}

# The {tidymodels} method for logistic regression requires that the response be a factor variable
resume <- resume %>% 
  mutate(received_callback = as.factor(received_callback))

resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)

```

```{r}
#logistic regression model
model <- glm(received_callback ~ ., data = resume, family = binomial())

#coefficients
coeff <- coef(model)

print(model)

```
