---
title: "Activity 6 - Multinomial Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "multinomial logistic regression model"
author: "Durga"
date: "7/22/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load the packages and libraries:

- Loading {tidyverse} and {tidymodels} as required for Multinomial regression


```{r}
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(dplyr)

```

#Load the data, create a datafram and organize the dataset

- Selecting only specific variables (ppage, educ, race, gender, income_cat, Q30, voter_category) from the created Dataframe

- Renaming variable Gender to Sex


```{r}

voters <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/non-voters/nonvoters_data.csv")


voters <- voters %>%
  select(ppage, educ, race, Sex = gender, income_cat, Q30, voter_category)

voters


```


- To create a new variable "party" with Q30 categories given

```{r}

# Assuming 'Q' is the variable representing the political preference

# Create a new variable 'political_party' based on the values of 'Q'
voters$party <- ifelse(voters$Q30 == 1, "Republican",
                                    ifelse(voters$Q30 == 2, "Democrat",
                                           ifelse(voters$Q30 == 3, "Independent",
                                                  ifelse(voters$Q30 == 4, "Another party, please specify",
                                                         ifelse(voters$Q30 == 5, "No preference", NA)))))

voters$party

```




```{r}

# Convert 'voter_category' to a factor
voters$voter_category <- factor(voters$voter_category)

# Now, fit the multinomial regression model
multi_mod <- multinom_reg() %>%
  set_engine("nnet") %>%
  fit(voter_category ~ ppage + educ + race + Sex + income_cat, data = voters)

multi_mod
```




```{r}

multi_mod$fit$call
nnet::multinom(formula = voter_category ~ ppage + educ + race + Sex + income_cat, data = voters, trace = FALSE)

```




```{r}

multi_mod <- repair_call(multi_mod, data = voters)
multi_mod$fit$call
nnet::multinom(formula = voter_category ~ ppage + educ + race + Sex + income_cat, data = voters, trace = FALSE)

```



```{r}
voter_aug <- augment(multi_mod, new_data = voters)

voter_aug

voter_aug %>% 
  select(contains("pred"))


```


```{r}

voter_conf_mat <- voter_aug %>% 
  count(voter_category, .pred_class, .drop = FALSE)

voter_conf_mat %>% 
  pivot_wider(
    names_from = .pred_class,
    values_from = n
  )

```


```{r}

voters %>% 
  ggplot(aes(x = voter_category)) +
  geom_bar() +
  labs(
    main = "Self-reported voter category"
    )

voter_conf_mat %>% 
  ggplot(aes(x = voter_category, y = n, fill = .pred_class)) +
  geom_bar(stat = "identity") +
  labs(
    main = "Predicted vs self-reported voter category"
    )

```



```{r}

# Assuming you have a dataset named 'voters' with 'voter_category' and 'party' as columns

# Convert 'voter_category' to a factor
voters$voter_category <- factor(voters$voter_category)

# Fit the multinomial regression model with additional predictor 'party'
multi_mod_with_party <- multinom_reg() %>%
  set_engine("nnet") %>%
  fit(voter_category ~ ppage + educ + race + Sex + income_cat + party, data = voters)

# Plot the self-reported voter category
voters %>% 
  ggplot(aes(x = voter_category)) +
  geom_bar() +
  labs(main = "Self-reported voter category")

# Get the confusion matrix for the model with additional predictor 'party'
voter_conf_mat_with_party <- multi_mod_with_party %>% 
  conf_mat(data = voters)

# Plot the predicted vs. self-reported voter category with 'party'
voter_conf_mat_with_party %>% 
  ggplot(aes(x = voter_category, y = n, fill = .pred_class)) +
  geom_bar(stat = "identity") +
  labs(main = "Predicted vs self-reported voter category (with 'party')")


```


- The differences between the above two models for variable Party, voter category:

Model Performance
Interpretation
Variable Importance
Model Assumptions
Model Complexity

